Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-15 paper/main.tex
Fixes to make the manuscript build
Some notes

\section{Introduction}

\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;
intro is about 1k words (with to dos)}

@@

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of faces
\citep{kanwisher1997ffa} or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.\todo{kinda aggressive introductory
sentence}.
% What is the PPA?
A classic example of a functionally defined, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes, buildings or landmarks \citep{aguirre1998area,
epstein2014neural, epstein1998ppa} compared to e.g. pictures of tools of faces.
% spatial layout hypothesis
[[According to the spatial layout hypothesis, the PPA is involved in processing
the surface geometry of a visual stimulus and possibly in identifying scenes
based on their spatial layout \citep{epstein2010reliable}.]]\todo{better delete}
% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

@@

% Wolbers: haptic exploration
In the block design study conducted by \cite{wolbers2011modality} the PPA of
sighted participants showed increased activation during a delayed
matching-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to haptically explored abstract geometric objects.
% connectivity analysis by Wolbers
\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
cortex, and compares connectivity during visual and haptic paradigm: ``The
scene-related increase in coupling with the PPA was significantly stronger in
multiple clusters in occipital cortex under visual than haptic stimulation
(Figure 2B; Table S2)''}

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% shortcomings of previous studies: simplified stimuli
Nevertheless, all reviewed studies have in common that they employed a small set
of simplified stimuli to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
Further, they usually relied on explicit judgment-based tasks to ensure that
participants payed attention to the stimuli.
% disadvantage 1b: lack of validity
Paradigms using block designs accompanied with a task have the disadvantage that
they do not resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2a: averaging for group results
Additionally, the reviewed studies averaged results across 7-11 subjects to
improve the signal-to-noise-ratio (SNR).
% disadvantage 2b: no individual level
The disadvantage here is that the averaging approach does not characterize brain
functions at an individual level, a prerequisite for the application of brain
imaging methods in individual diagnostics (cf. \cite{dubois2016building,
eickhoff2020towards}).
% open questions
This raises the question how the PPA behaves under life-like conditions, and how
group results a driven by individuals subjects especially in response to
audio-only stimulation\todo{``audio-only'' sounds meh?}.

@@

% what we did: data source
In the current study, we analyze publicly available functional data
(studyforrest.org) of the same 14 participants watching a movie
\citep{hanke2016simultaneous} and listening to an audiobook.
\citep{hanke2014audiomovie}.
% PPA + movie + audio-description
We annotated cuts in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during more life-like
conditions free from any task.
% traditional GLM
We do this by analyzing our data by constructing GLM contrasts as canonically
used to analyze data from tightly controlled paradigms.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
an audio-only paradigm. We further test the audio-description's localization
performance of a ``visual area'' in individual study participants by comparing
our results to results of a dedicated visual localizer experiment done with the
same participants \citep{sengupta2016extension}.
% results
Our results demonstrate that (a), (b), (c)... \todo{similar to abstract and
conclusion}

@@

% we did a couple of contrasts and why
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to test the stability of results across different
contrasts and exclude accidental findings.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
% selection of the primary contrast
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.

\todo[inline]{compare the following with annotation \& Discussion}
% intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for a couple of reasons and thus are not
included in the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``black and white film
recordings'', ``in Greenbow'') whereas a picture of the verbally described scene
would be perceptually richer,
% hierarchical categories
(b) They also comprise words that could count as a member of another categories
in case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as teenager'', ``near and old bus'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.
cuts but in AO stimulus}
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.

@@

% intro
In context of the AV stimulus, we categorized the frames following a movie cut
irrespective of their concrete visual content and thus without controlling
confounding variables (e.g. presence of faces). The rationale that this
procedure would still be able to isolate the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is greater
when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% hence, the following contrasts
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}).
\todo[inline]{all null results; except cope 10 (nouns of narrator but in movie):
right PPA, bilat sup. lat. occ. cortec, LOC (l/r), right superior parietal
lobe).

>>>>

\section{Introduction}
\todo[inline]{I wonder whether we should make a general point: The construction
  of contrasts of interests feels "messy". But this is a consequence of the
  inability to filter the stimulus material. That "messy" part is usually not obvious from a manuscript.
  Here we have a fixed, complex stimulus, and we have to operationalize our questions with whatever we
have at hand. This is not necessarily exact, and looking at the robustness is a feature, not a problem}
\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;
intro is about 1k words (with to dos)}

@@

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of faces
\citep{kanwisher1997ffa} or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.\todo{kinda aggressive introductory
sentence}.
% What is the PPA?
A classic example of a functionally defined, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes, buildings or landmarks \citep{aguirre1998area,
epstein2014neural, epstein1998ppa} compared to e.g. pictures of tools of faces.
% spatial layout hypothesis
[[According to the spatial layout hypothesis, the PPA is involved in processing
the surface geometry of a visual stimulus and possibly in identifying scenes
based on their spatial layout \citep{epstein2010reliable}.]]\todo{better delete}
% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize \todo{MIH: more specific? what generalizes? just some location?} to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

@@

% Wolbers: haptic exploration
In the block design study conducted by \cite{wolbers2011modality} the PPA of
sighted participants showed increased activation during a delayed
match-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to haptically explored abstract geometric objects.
% connectivity analysis by Wolbers
\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
cortex, and compares connectivity during visual and haptic paradigm: ``The
scene-related increase in coupling with the PPA was significantly stronger in
multiple clusters in occipital cortex under visual than haptic stimulation
(Figure 2B; Table S2)''}

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% shortcomings of previous studies: simplified stimuli
Nevertheless, all reviewed studies have in common that they employed a small set
of simplified stimuli to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
Further, they usually relied on explicit judgment-based tasks to ensure that
participants payed attention to the stimuli.
% disadvantage 1b: lack of validity
Paradigms using block designs accompanied with a task have the disadvantage that
they do not resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2a: averaging for group results
Additionally, the reviewed studies averaged results across 7-11 subjects to
improve the signal-to-noise-ratio (SNR).
% disadvantage 2b: no individual level
The disadvantage here is that the averaging approach does not characterize brain
functions at an individual level, a prerequisite for the application of brain
imaging methods in individual diagnostics (cf. \cite{dubois2016building,
eickhoff2020towards}).
% open questions
This raises the question how the PPA behaves under life-like conditions, and how
group results a driven by individuals subjects especially in response to
audio-only stimulation\todo{``audio-only'' sounds meh?, MIH: Yes, and comes out of nowhere}.

@@

% what we did: data source
In the current study, we analyze publicly available functional data
(studyforrest.org) of the same 14 participants watching a movie
\citep{hanke2016simultaneous} and listening to an audiobook.
\citep{hanke2014audiomovie}.
% PPA + movie + audio-description
We annotated cuts \todo{MIH: only cuts relevant?} in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during more life-like
conditions free from any task.
% traditional GLM
We do this by analyzing our data by constructing GLM contrasts as canonically
used to analyze data from tightly controlled paradigms.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
an audio-only paradigm. We further test the audio-description's localization
performance of a ``visual area'' in individual study participants by comparing
our results to results of a dedicated visual localizer experiment done with the
same participants \citep{sengupta2016extension}.
% results
Our results demonstrate that (a), (b), (c)... \todo{similar to abstract and
conclusion}

@@

% we did a couple of contrasts and why
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to test the stability of results across different
contrasts and exclude accidental \todo{MIH: what does this mean? exclude incidental findings? sounds like we made it look pretty...} findings.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
% selection of the primary contrast
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.

\todo[inline]{compare the following with annotation \& Discussion}
% intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for a couple of reasons and thus are not
included in the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``black and white film
recordings'', ``in Greenbow'') whereas a picture of the verbally described scene
would be perceptually richer,
% hierarchical categories
(b) They also comprise words that could count as a member of another categories
in case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as teenager'', ``near an old bus'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.
cuts but in AO stimulus
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.

@@

% intro
In context of the AV stimulus, we categorized the frames following a movie cut
irrespective of their concrete visual content and thus without controlling
confounding variables (e.g. presence of faces). The rationale that this
procedure would still be able to isolate the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was simply that activity in the PPA is greater
when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% hence, the following contrasts
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}).
\todo[inline]{all null results; except cope 10 (nouns of narrator but in movie):
right PPA, bilat sup. lat. occ. cortec, LOC (l/r), right superior parietal
lobe).}
